\subsubsection{Proposed Changes}
For use in our service, this R package needs to be modified. Namely, the Bioacoustic index and AEI outputs need to be more detailed. For Bioacoustic, the bioacoustic values for both the left and right channels needed to be output, along with the normalized left and right channel values. These values are in turn used in our visualizations to create the area graphs shown in the Data Visualizations Research section. As for AEI, it just needed to be changed to match that of the ADI. For whatever reason, the core package output only the AEI values for the left and right channel, and did not output the left and right band values and left and right band ranges. These are also used in the AEI and ADI visualizations.\par
Another proposed change that is talked about a bit in the Benchmarking section, is that of file size constraints. Currently, certain indices are not able to be computed on long files due to hardware limitations even on high end systems. These memory issues are the result of matrices being created in indices like ACI. From reviewing the code, these matrices are being used as intermediary values used in the calculation of lists of \textit{more} intermediary values. These matrices are in fact output to the user, however the usefullness of them is up for debate. Proposed changes to circumvent these issues includes possible removing these matrices, or adding a file splicing feature. Files that are over a certain length would need to be split into equal length parts, and the index calculated on each. From there, the overall index value could be calculated either in R or in the client.
