\subsection{Permissions}
\subsubsection{Users}
This application will have several users, spanning across multiple organizations. Many of these users will have a vast amount of data that they will wish to keep secure if they are to use the application. The problem comes when the data that users have stored needs to become outward facing. Examples of this include requests to pull files, accumulating data for crowd sourced visualizations, or showing snippets of interesting sound files to other users. In general, this application revolves around public data and the visualization of that data. For this very reason, we must ensure that user data is kept secure and that we have the trust of our users when implementing this software.\par
The basis of data security in this project will stem from the use of Universally Unique Identifiers. These UUID\textquotesingle s are randomly generated hexadecimal character strings that can be used to identify users, groups, jobs, and so on. While rate of collision using this method is not zero, the occurrence is so seldom that checking is not required. Users will be assigned an identifier once they install the software and create a login. From that point forward, all user activity will be tracked using the randomly assigned identifier and the user\textquotesingle s email, which will be required in order to authenticate. Combining email and UUID provides an astronomically low chance of collisions. This will allow tracking of all user actions. Thus, ensuring that from the point of first use, no creation or manipulation of data can be performed without the proper user being connected to the action. This will allow for accountability to be held to the end user in case a malicious action is taken to destroy, obscure, or otherwise harm data through our application.\par
By taking account of all users with these methods, we can then very easily set up permissions for each file or sets of files that are publicly facing through the application. The database will map files to the selected users that can see them. This will be cross-validated by also keeping track of what users can see the files. Both table entries must match for the file to be accessed by the requesting user.
