\subsubsection{Large File Analysis}

\paragraph{System 1: Intel i5 6500 4 Cores @ 3.2GHz / 16GB RAM} \mbox{}\\[\paragraphheaderspace]
The analysis took 686.64 seconds to process a single 1.29GB wav sound file. That comes out to 1.29GB in eleven minutes and forty four seconds. For a data set comprised of one hundred 1.29GB sound files, that would estimate to around nineteen hours for 129GB of sound files.

\paragraph{System 2: Intel i7 7500U 2 Cores @ 2.7GHz / 16GB RAM} \mbox{}\\[\paragraphheaderspace]
The analysis took 1045.95 seconds to process a single 1.29GB wav sound file. That comes out to 1.29GB in seventeen minutes and twenty five seconds. For a data set comprised of one hundred 1.29GB sound files, that would estimate to around twenty nine hours for 129GB of sound files.

\paragraph{System 3: Intel i5 5200U 2 Cores @ 2.2GHz / 8GB RAM} \mbox{}\\[\paragraphheaderspace]
The process of converting this single wav file to a Wave object in R actually managed to freeze this system for around 30 minutes, before any analysis even began. Then after 315.4 seconds, a little over five minutes, the processing stopped with an error reading "cannot allocate vector of size 1.3GB." This was an unexpected result, raising questions as to possible user minimum required hardware specs. Thus, with this hardware, processing is not even feasible.

\paragraph{System 4: Intel i7 6500U 4 Cores @ 3.1GHz / 24GB RAM} \mbox{}\\[\paragraphheaderspace]
The analysis took 585.19 seconds to process a single 1.29GB wav sound file. That comes out to 1.29GB in nine minutes and forty five seconds. For a data set comprised of one hundred 1.29GB sound files, that would estimate to around sixteen hours for 129GB of sound files.

\paragraph{System 5: Intel i7 7700HQ 4 Cores @ 2.8GHz / 16GB RAM} \mbox{}\\[\paragraphheaderspace]
The analysis took 690 seconds to process a single 1.29GB wav sound file. That comes out to 1.29GB in eleven minutes and thirty seconds. For a data set comprised of one hundred 1.29GB sound files, that would estimate to around nineteen hours for 129GB of sound files.

\paragraph{System 6: Intel i5 5200U 4 Cores @ 2.7GHz / 8GB RAM} \mbox{}\\[\paragraphheaderspace]
This system also could not manage to process the sound file due to memory issues. Again, processing with these specs is infeasible.

\paragraph{Solutions} \mbox{}\\[\paragraphheaderspace]
A solution to the issue of memory problems and processing time is the splitting of sound files into smaller pieces. Currently, each file is sixty minutes long. The sample file used was cut into six, ten minute parts, still retaining the wav file type. The NDSI processing time improved a bit on System 1, with each file taking  about 102.41 seconds, coming to about ten minutes. Further, when attempting to run the ACI index on System 1 \textit{without} splitting the file, it could not be done due to memory issues, even at 16GB of RAM. However when splitting the file, not only could the processing occur succesfully, it did so in 29.33 seconds, almost three minutes for all six files. This is much more reasonable and successful all around, and will be implemented into the service. Luckily the \codesnip{soundecology} package includes parameters for splitting up large files into smaller sections for analysis, which solves some of these issues.
