\subsection{Statements of Motivation}
\noindent\textit{David Palumbo} ---
\begin{quote}
``I chose this project primarily because it falls under some of my career interests, those being big data analysis, data visualization, and machine learning. These are three areas I\textquotesingle ve found myself gravitating toward as I move from the end of my schooling into the workforce, and this project would enable me to develop my skills in each. Additionally, the project has the potential to create a positive impact on the environment by creating a tool to be used by researchers in the field of soundscape ecology, a cutting-edge field that looks to study the relationship between living organisms and the sounds produced by these organisms and their environments. There are few tools available to these researchers, and of those that exist, the majority are not open-source. If I can help create software that simplifies the work of soundscape ecologists, then in doing so I can help accelerate the pace of scientific progress.''
\end{quote}

\noindent\textit{Keith Guske} ---
\begin{quote}
``When selecting projects, I had three criteria in mind:
\begin{enumerate}
  \item Amount of impact the project would have
  \item Current experience with necessary technologies
  \item Interest in learning about new technologies necessary for the projects
\end{enumerate}
With that in mind, this project balanced all three criteria as it could allow anyone to assist in sound ecology research and conservation, I have experience in R and UI/UX design, and I would love to figure out how I could approach parsing 8TB of sound files. While there were other projects that met some of these criteria, (notably the Red Lobster projects, the data compression research, and \lq How Dare You Charge Me \$15 More a Year for a Hang Tag\rq), none other met all three. With that said, I\textquotesingle m glad I got my first choice project.''
\end{quote}

\noindent\textit{Brita Ramsay} ---
\begin{quote}
``This project initially caught my interest when I heard Dr. Beever\textquotesingle s overview of the field of Soundscape Ecology. It is a very unique approach to researching environmental conservation. There also seemed to be many interesting possibilities for creating data visualizations that would be very useful to researchers. The requirements of project seemed to be pretty balanced as to topics I am already familiar with and new ideas that I would like to explore. I have experience making full stack web applications and thought that some of that could be applied to this project. I did not want to choose a project with requirements that would be completely new to me. The machine learning stretch goals of the project also motivated me to choose this project. I would really like learn more about this topic and hopefully be able to apply machine learning to help Soundscape Ecologists in their research.''
\end{quote}

\noindent\textit{Josh Pollmann} ---
\begin{quote}
``My personal interest in this project stems from an interest in big data and machine learning. Dr. Beever did a great job pitching the unique field that is soundscape ecology so I was immediately interested in the project. He also mentioned that the research was pretty new so whatever became of this project would be one of a kind. So, the prospect of creating something new and unique that hasn\textquotesingle t been done before all while including my career interests is what really drew me to do this project. I also believe that the data that will be able to be analyzed using our end product will be highly valuable to environmental research and conservation efforts in the future, implicating a much broader impact outside of my own career.''
\end{quote}

\noindent\textit{Ot Gabaldon Torrents} ---
\begin{quote}
``The involvement with nature is the first thing that caught my eye when this project was announced. I have loved everything nature has to offer for as long as I remember. As Dr. Beever went on with his presentation he started to mention the preservation of the environment through machine learning methods. That\textquotesingle s when I realized this project would be one that I could connect with on a both professional and personal levels. By combining my interest in artificial intelligence and love for the environment I think my contribution to this project will be both genuine and motivated by personal interests. If this project succeeds I believe that it can make a large difference in not only the soundscape ecology of florida but in the world as well. By allowing researchers to compare their results and see those results in a simpler and more defined way; the soundscape community can arrive efficiently to solutions that might have been to convoluted to see before.''
\end{quote}
