\subsection{Budgeting and Finances}
We have decided to allocate the processing to the user\textquotesingle s local hardware, therefore no expenses on our end is needed for that aspect of the project. When it comes to collaborative resources for users along with interfacing between our servers and application/website, this will require some small but potential expenses. Plans involving AWS servers are going to require, at most, \$1-\$3 a month for AWS services according to Amazon. Lambda use is priced at \$0.20 per one million requests after the first one million, according to Amazon. We currently cannot estimate the number of requests needed for our actual processing, however we have predicted it to be at most \$30 a month, however this prediction is believed a bit generous. The sponsor has not allocated any funds, however grants are possible should the need arise. Thus, any expenses would have to come out of the team\textquotesingle s pocket and possibly the sponsor should they agree.\par
Amazon provides an AWS cost calculator to estimate costs for using their sevices. For S3 storage, at 5GB of storage, 50,000 POST and SELECT requests, and 18TB of return data and scanned data, it would cost \$16.47 per month. This cost is seemingly small especially when split among the team and sponsor and potentially other end users. However we use this 18TB benchmark because our sponsor currently has about this much space in sound files stored locally. This issue with this is that if we scale up to 180TB of storage to account for just ten other users, and also increase the return and scan data space to 180TB, this cost increases to \$4606.81. This cost is infeasible for the project and played a part in our decision to use DynamoDB in addition to the NoSQL properties of DynamoDB.\par
As for DynamoDB, using the AWS cost calculator, for storing 180TB of data it would cost \$50576.27 a month. Again, this cost is infeasible. Thus the decision to disallow users from storing sound files was made. It is simply impossible for the scope of this project to allow users to store the massive amount of data that sound files present. Instead, users will upload analysis they have done. This is a generous estimat of about 1.3MB of data per person, and for 100 users, this cost comes to \$2.52 per month, a much more feasible cost for everyone involved.\par
Amazon\textquotesingle s Lambda service is an option for the user to run fast processing on their data set, but at a cost. It is estimated that at 500 executions, with just 128MB of allocated memory, that a 10 hour processing job would cost \$38.34 a month. This again is a generous estimate, but is a bit more substantial than the DyanmoDB costs. Thus we have decided that this cost must be delegated to the end user should they choose to take on these costs.
