\subsection{Facilities \& Equipment}
\subsubsection{Facilities}
\textbf{UCF Arboretum}\\
The UCF arboretum was created in 1983 as a place for students and faculty to learn about ecology and work with the environment. The arboretum acts as a research area on campus for identifying plants and the local wildlife
\cite{ucfarboretum}. Our sponsor, Dr. Beever, has been conducting research in the arboretum and surrounding areas to get a better understanding of the impact of humans on the local ecosystem.\\\\
\textbf{Central Florida Zoo}\\
<Something here about the zoo>\\

\subsubsection{Equipment}
\textbf{QNAP}\\
Our sponsor has access to a device called a QNAP. A QNAP acts as a local storage device but also as a remote server when needed. This device is useful for our project because it gives us access to a sort of private server option for our users, if they would prefer not to use a OneDrive service or something similar. In using a QNAP or other private device, the users can specify files and folders for others to access and provide those access rights to our service for others to use. The QNAP is also handy because it provides a built in interface for users to tap into and easily find the files being offered by the provider.\\\\
\textbf{Microphones}\\
Some important equipment used by the researchers in the field of soundscape ecology include microphones. Our sponsor in particular uses a Wildlife Acoustics SM4 model along with the Wildlife Acoustics Song Meter device.\par
The Song Meter is considered the smallest and lightest dual channel acoustic recorder available\cite{songmeter}. The microphones record raw sound and store them in uncompressed .wav files. These .wav files can then be used by programs like ours to calculate the indices mentioned for analysis by researchers.\par
Our sponsor\textquotesingle s strategy is to place these microphones in multiple places in the environment being tested, to get a better understanding of the impact of sound on the ecosystem. In doing this, we can hear more of the sounds of the ecosystem and provide better index analysis.\par